An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-08 scagnostics.Rmd
Changed timing code, added result.

>>>>

## Note on calculation time
Computing time differs for each index, and depends strongly on the number of data points (as well as probably some dependence on distribution type), here we use as an example the 6-d sphere and calculate the computing time for different indices over 100 interpolated grand tour projections as a function of the sample size.

```{r getTimer}

mineE <- function(x,y){
  return(mine(x=x, y=y, est = "mic_e"))
}

timeThis <- function(d, t, idx, pmax){ #d=data matrix, t=interpolated tour path, idx=index function, pmax=max number of projections
    i <- 1
    tic.clearlog()
    tic() #start timer
    for(pMatrix in t){
      if(i>pmax) break
      dProj <- d %*% pMatrix
      sgnst <- idx(dProj[,1],dProj[,2])
      i = i+1
    }
    toc(log=TRUE,quiet=TRUE)
    scTd <- unlist(tic.log(format=FALSE))["toc.elapsed"]-unlist(tic.log(format=FALSE))["tic.elapsed"]
}

```

```{r timer}
if(!file.exists("cache/timer.rda")){
  set.seed(2018)
  grandTour100 <- save_history(sphere100, grand_tour(2), max=4) %>%
    interpolate() %>%
    as.list()

  sizeL <- c(10, 100, 500, 1000, 5000, 10000)
  n <- length(sizeL)
  dfTimer = data.frame( n=rep(0, n), scagT=rep(0,n), dcorT=rep(0,n), splineT=rep(0,n), mineT=rep(0,n),
                        mineeT=rep(0,n))
  t <- 1
  for(sampleSize in sizeL){
    set.seed(sampleSize + 11) # new seed for each sample size
    if(sampleSize == 0) sampleSize = 10 # smallest considered sample has 10 points
    thisMatrix <-  sphereData(6, sampleSize) %>% rescale()
    scagT <- timeThis(thisMatrix, grandTour100, scagnostics.default, 100)
    dcorT <- timeThis(thisMatrix, grandTour100, dcor2d, 100)
    splineT <- timeThis(thisMatrix, grandTour100, splines2d, 100)
    mineT <- timeThis(thisMatrix, grandTour100, mine, 100)
    mineeT <- timeThis(thisMatrix, grandTour100, mineE, 100)
    dfTimer[t,] <- c(sampleSize, scagT, dcorT, splineT, mineT,mineeT)
    t <-  t+1
  }
  save(dfTimer, file = "cache/timer.rda")
} else {
  load("cache/timer.rda")
}

timerMelt <- melt(dfTimer, id="n")
ggplot(timerMelt, aes(x = n, y = value, color=variable)) + 
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Sample Size", y = "Time [s]", color = "Index family")
```
